\documentclass[letterpaper,10pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{slantsc}  
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{tabto}


\usepackage{graphicx}
\graphicspath{ {images/}} 
\usepackage[left=0.5in, right=0.5in, bottom=1in, top=1in]{geometry}

%%HEADER

\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\rhead{\textit{Updated \today}}
\lhead{\Large{\textsc{David C. Mallinson, PhD}}}
\cfoot{Page \thepage}

\newcounter{example}[section]
\newenvironment{example}[1][]{\refstepcounter{example}%\par%\medskip
   \textbf{[\theexample]} \rmfamily}%{\medskip}

\begin{document}

%%CONTACT
\begin{longtable}{@{} p{0.15\textwidth} p{0.9\textwidth}}
%\noindent \begin{longtable}{@{} l l}
\textsc{Contact}   & Department of Family Medicine \& Community Health\\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & 610 N Whitney Way \\
     & STE 200 \\
     & Madison, WI 53705 \\
     & \\
     & Email: dmallinson@wisc.edu \\
     & Web: \href{https://davidmallinson.github.io}{https://davidmallinson.github.io} \\
     & ORCID: \href{https://orcid.org/0000-0003-1069-6040/}{0000-0003-1069-6040} \\
     & \\
%%EDUCATION
\textsc{Education}    & \textbf{University of Wisconsin-Madison School of Medicine and Public Health} \\
     & PhD, Population Health Sciences, 2021 \\
     & \parbox{6.15in}{\underline{Dissertation:} Sibling spillover effects: method and applications} \\
     & \parbox{6.15in}{\underline{Committee:} Deborah Ehrenthal (co-chair), Felix Elwert (co-chair, Sociology), John Mullahy, Paul Peppard} \\
     & \\
     & \textbf{Dartmouth College} \\
     & MS, Healthcare Research, 2015 \\
     & \\
     & \textbf{College of Wooster} \\
     & BA, Communication Studies, Economics, 2013 (\textit{cum laude}) \\
     & \\
%%EMPLOYMENT
\textsc{Employment} & Postdoctoral Fellow, September 2022-Present \\
     & Department of Family Medicine \& Community Health \\
     & University of Wisconsin-Madison \\
     & \\
     & Postdoctoral Fellow, August 2021-August 2022 \\
     & Population Research Center \\
     & University of Texas-Austin \\
     & \\
%%RESEARCH AREAS
\textsc{Research}   &\textbf{Areas} \\
    & \\
    & \parbox{6.15in}{\underline{Substantive:} Infant health and development. Maternal and child health epidemiology. Prenatal and pediatric health care surveillance and evaluation.} \\
    & \\
    & \parbox{6.15in}{\underline{Methodological:} Graphical causal modeling. Multi-level modeling. Sibling comparison designs. Spillover effects.} \\
    & \\
%%GRANTS
    &\textbf{Grants} \\
    & \\
    & \parbox{6.15in}{``Racial and Geographic Disparities of Prenatal Care Coordination in Wisconsin."} \\
    & \parbox{6.15in}{\hspace*{1.5em}\underline{Role:} Primary Investigator} \\
    & \parbox{6.15in}{\hspace*{1.5em}\underline{Award:} Advancing Health Equity and Diversity Pilot Award} \\
    & \parbox{6.15in}{\hspace*{1.5em}\underline{Source:} Institute for Clinical and Translational Research, University of Wisconsin-Madison} \\
    & \parbox{6.15in}{\hspace*{1.5em}\underline{Support:} \$10,000, July 2023-June 2024} \\
    & \\
%%PUBLICATIONS
    &\textbf{Peer-Reviewed Publications} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Gillespie KH (2024). Racial and geographic variation of Prenatal Care Coordination receipt in the state of Wisconsin, 2010-2019. \textit{Journal of Community Health}. [Forthcoming] \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F, Ehrenthal DB (2024). Spillover effects of gestational age on sibling’s literacy. \textit{Early Child Development and Care}. \href{https://doi.org/10.1080/03004430.2023.2301420}{\underline{https://doi.org/10.1080/03004430.2023.2301420}} [Online ahead of print] \\ \textit{*Finalist, SER Tyroler Prize Paper Award, 2022 [preliminary draft]} \end{example}} \\
    %& \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F, Ehrenthal DB (2023). Spillover effects of Prenatal Care Coordination on older siblings beyond the mother-infant dyad. \textit{Medical Care}. 61(4):206-215. \href{https://doi.org/10.1097/mlr.0000000000001822}{\underline{https://doi.org/10.1097/mlr.0000000000001822}} \\ \textit{*Recipient, UW-Madison DFMCH William E. Scheckler Award, 2024}  \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Marteleto LJ, Dondero M, Kumar S, \textbf{Mallinson DC} (2023). Measuring fertility intentions during times of crisis: an example using survey data amid the Covid-19 pandemic. \textit{Studies in Family Planning}. 54(1):161-180. \href{https://doi.org/10.1111/sifp.12219}{\underline{https://doi.org/10.1111/sifp.12219}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Coutinho RZ, Firmino B, \textbf{Mallinson DC} (2022). ``Exploring the Effects of Covid-19 on the Lives of Brazilian Women: Results of a National Online Survey." In: Hubert C, Miranda-Ribeiro P, Salinas V, editors. \textit{Fecundidad, salud sexual y reproductiva en tiempos de la COVID-19 en Latinoamérica} [\textit{Fertility, sexual and reproductive health in times of COVID-19 in Latin America}]. Rio de Janeiro, BR: ALAP Press; 38-66.  \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Rubenstein E, Ehrenthal DB, Nobles J, \textbf{Mallinson DC}, Bishop L, Jenkins MC, Kuo H, Durkin MS (2022). Brief report: Fertility rates in women with intellectual and developmental disabilities in Wisconsin Medicaid. \textit{Disability and Health Journal}. 15(3):101321. \href{https://doi.org/10.1016/j.dhjo.2022.101321}{\underline{https://doi.org/10.1016/j.dhjo.2022.101321}}   \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F (2022). Estimating sibling spillover effects with unobserved confounding using gain-scores. \textit{Annals of Epidemiology}. 67(March 2022):73-80. \href{https://doi.org/10.1016/j.annepidem.2021.12.010}{\underline{https://doi.org/10.1016/j.annepidem.2021.12.010}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Rubenstein E, Ehrenthal DB, \textbf{Mallinson DC}, Bishop L, Kuo H, Durkin M (2021). Birth outcomes affecting infants of mothers with intellectual and developmental disabilities. \textit{Paediatric and Perinatal Epidemiology}. 35(6):706-716. \href{https://doi.org/10.1111/ppe.12765}{\underline{https://doi.org/10.1111/ppe.12765}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Rubenstein E, Ehrenthal DB, \textbf{Mallinson DC}, Bishop L, Kuo H, Durkin M (2020). Pregnancy complications and maternal birth outcomes in women with intellectual and developmental disabilities in Wisconsin Medicaid. \textit{PLOS ONE}. 15(10):e0241298. \href{https://doi.org/10.1371/journal.pone.0241298}{\underline{https://doi.org/10.1371/journal.pone.0241298}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Larson A, Berger LM, Grodsky E, Ehrenthal DB (2020). Estimating the effect of Prenatal Care Coordination in Wisconsin: a sibling fixed effects analysis. \textit{Health Services Research}. 55(1):82-93. \href{https://doi.org/10.1111/1475-6773.13239}{\underline{https://doi.org/10.1111/1475-6773.13239}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Grodsky E, Ehrenthal DB (2019). Gestational age, kindergarten-level literacy, and effect modification by maternal socio-economic and demographic factors. \textit{Paediatric and Perinatal Epidemiology}. 33(6):467-479. \href{https://doi.org/10.1111/ppe.12588}{\underline{https://doi.org/10.1111/ppe.12588}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kamenetsky ME, Hagen EW, Peppard PE (2019). Subjective sleep measurement: comparing sleep diary to questionnaire. \textit{Nature and Science of Sleep}. 11:197-206. \href{https://doi.org/10.2147/NSS.S217867}{\underline{https://doi.org/10.2147/NSS.S2178678}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Ehrenthal DB (2019). Classification of Medicaid coverage on births records in Wisconsin, 2011-2012. \textit{Public Health Reports}. 134(5):542-551. \href{https://doi.org/10.1177/0033354919860503}{\underline{https://doi.org/10.1177/0033354919860503}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Ozanne EM, Howe R, \textbf{Mallinson D}, Esserman L, van’t Veer LJ, Kaplan CP (2019). Evaluation of National Comprehensive Cancer Network guideline‐based Tool for Risk Assessment for breast and ovarian Cancer (N‐TRAC): a patient‐reported survey for genetic high‐risk assessment for breast and ovarian cancers in women. \textit{Journal of Genetic Counseling}. 28(3):507-515. \href{https://doi.org/10.1002/jgc4.1051}{\underline{https://doi.org/10.1002/jgc4.1051}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Larson A, Berger LM, \textbf{Mallinson DC}, Grodsky E, Ehrenthal DB (2019). Variable uptake of Medicaid-covered Prenatal Care Coordination: the relevance of treatment level and service context. \textit{Journal of Community Health}. 44(1):32-43. \href{https://doi.org/10.1007/s10900-018-0550-9}{\underline{https://doi.org/10.1007/s10900-018-0550-9}} \end{example}} \\
   % & \\
    %& \\
    %%UNDER REVIEW
    & \setcounter{example}{0} \\
    &\textbf{Under Review} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kuo H, Kirby RS, Wang Y, Berger LM, Ehrenthal DB. Maternal opioid use disorder and infant mortality in Wisconsin, 2010-2018. [Revised and resubmitted] \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}. Prenatal Care Coordination and its impact on well-child visit receipt in early childhood. \end{example}} \\																	
    %& \\
    %%IN PROGRESS/PREPRINTS
    & \setcounter{example}{0} \\
    &\textbf{Preprints} \\
    %& \parbox{6.15in}{\begin{example} Dondero M, \textbf{Mallinson DC}, Marteleto LJ. The Zika epidemic as a prenatal stressor: maternal exposure to the Zika epidemic and birth outcomes in Brazil. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}. Assessing outcome-to-outcome interference in sibling fixed effects models. Preprint: \href{https://arxiv.org/abs/2109.13399}{\underline{https://arxiv.org/abs/2109.13399}} \end{example}} \\
    %& \\
    %%LETTERS/OPINIONS
    & \setcounter{example}{0} \\
    &\textbf{Letters and Opinions} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC} (2022). The opportunities of change score analyses. \textit{International Journal of Epidemiology}. 51(5):1690-1691. \href{https://doi.org/10.1093/ije/dyab201}{\underline{https://doi.org/10.1093/ije/dyab201}} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC} (2018). Disparities in hospital readmissions. \textit{Health Affairs}. 37(8):1340. \href{https://doi.org/10.1377/hlthaff.2018.0552}{\underline{https://doi.org/10.1377/hlthaff.2018.0552 }}\end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kramer RD, Mohamoud YA (2018). Challenges in studying Medicaid expansion's association with infant mortality. \textit{American Journal of Public Health}. 108(7):e24. \href{https://doi.org/10.2105/AJPH.2018.304486}{\underline{https://doi.org/10.2105/AJPH.2018.304486}}\end{example}} \\
    %%CONFERENCE WORKSHOPS
    & \setcounter{example}{0} \\
    &\textbf{Conference Workshops and Panels} \\
    & \\
    & \parbox{6.15in}{\begin{example} Kirby RS, Ehrenthal DB, \textbf{Mallinson DC}, Berger LM. Data integration and population-based maternal and child health. CityMatCH Leadership and MCH Epidemiology Conference (2020). Virtual conference. \end{example}} \\
    %%CONFERENCE ABSTRACTS
    & \setcounter{example}{0} \\
    &\textbf{Conference Abstracts} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kuo H, Kirby RS, Berger LM, Ehrenthal DB. Maternal opioid use disorder and infant mortality in Wisconsin, 2010-2018. Society for Epidemiologic Research Annual Meeting (2023). Portland, OR. Oral presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kuo H, Kirby RS, Berger LM, Ehrenthal DB. Maternal opioid use disorder and infant mortality in Wisconsin, 2010-2018. Society for Pediatric and Perinatal Epidemiologic Research Annual Meeting (2023). Portland, OR. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}. Assessing outcome-to-outcome interference in sibling fixed effects models. Population Association of America Annual Meeting (2023). New Orleans, LA. Oral presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Kuo H, Kirby RS, Berger LM, Ehrenthal DB. Maternal opioid use disorder and infant mortality in Wisconsin, 2010-2018. Population Association of America Annual Meeting (2023). New Orleans, LA. Oral presentation. [\textit{Forthcoming}] \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Marteleto LJ. Birth weight and subsequent pregnancy intention in the context of disease outbreaks. Population Association of America Annual Meeting (2022). Atlanta, GA. Oral presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F, Ehrenthal DB. Gestational age and siblings' literacy: spillover effects in the family. Society for Epidemiologic Research Annual Meeting (2021). Virtual conference. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Rubenstein E, Ehrenthal DB, Nobles J, \textbf{Mallinson DC}, Bishop L, Jenkins M, Kuo HD, Durkin M. Fertility rates in women with intellectual and developmental disabilities in Wisconsin Medicaid. Society for Pediatric and Perinatal Epidemiologic Research Annual Meeting (2021). Virtual conference. Oral presentation.  \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F, Ehrenthal DB. Society for Pediatric and Perinatal Epidemiologic Research Annual Meeting (2021). Virtual conference. Oral presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Elwert F, Ehrenthal DB. Gestational age and siblings' literacy: spillover effects in the family. Population Association of America Annual Meeting (2021). Virtual conference. Oral presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Ehrenthal DB. Prenatal Care Coordination and birth spacing among Medicaid beneficiaries in Wisconsin. Population Association of America Annual Meeting (2020). Washington, DC. Poster presentation. [Accepted — conference canceled due to 2020 COVID-19 disease outbreak] \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Grodsky E, Berger LM, Ehrenthal DB. Gestational age, early literacy, and effect modification by maternal socioeconomic or demographic factors. Society for Epidemiologic Research Annual Meeting (2019). Minneapolis, MN. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Grodsky E, Berger LM, Ehrenthal DB. Gestational age, early literacy, and effect modification by maternal socioeconomic or demographic factors. Society for Pediatric and Perinatal Epidemiologic Research Annual Meeting (2019). Minneapolis, MN. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Shrider EA, \textbf{Mallinson DC}. Evaluating rural-urban typologies for use in healthcare research. Population Association of America Annual Meeting (2019). Austin, TX. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Larson A, \textbf{Mallinson DC}*, Berger LM, Grodsky E, Ehrenthal DB. The effect of Prenatal Care Coordination on birth outcomes: a sibling fixed effects analysis. CityMatCH Leadership and MCH Epidemiology Conference (2018). Portland, OR. Oral presentation. \\
	\textit{*Presenter} \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Larson AM, Berger LM, \textbf{Mallinson DC}, Grodsky E, Ehrenthal DB. Variable uptake of Medicaid-covered Prenatal Care Coordination: the relevance of treatment level and service context. AcademyHealth Annual Research Meeting (2018). Seattle, WA. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} Ehrenthal DB, \textbf{Mallinson DC}, Larson AM, Voskuil K, Berger LM, Grodsky E. Integrating data systems to expand the evidence base for maternal and child health strategies. AcademyHealth Annual Research Meeting (2018). Seattle, WA. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Ehrenthal DB. Classification of Medicaid coverage on birth records in Wisconsin, 2011-2012. Society for Epidemiologic Research Annual Meeting (2017). Seattle, WA. Poster presentation. \end{example}} \\
    & \\
    & \parbox{6.15in}{\begin{example} \textbf{Mallinson DC}, Ehrenthal DB. Classification of Medicaid coverage on birth records in Wisconsin, 2011-2012. Society for Pediatric and Perinatal Epidemiologic Research Annual Meeting (2017). Seattle, WA. Poster presentation. \end{example}} \\ 
%%SERVICE
    & \setcounter{example}{0} \\
\textsc{Service}   &\textbf{Journal Referee} \\
    & \parbox{6.15in}{\textit{American Journal of Epidemiology}, \textit{American Journal of Public Health}, \textit{Health Affairs}, \textit{Health Services Research}, \textit{International Journal of Women's Health}, \textit{Medical Care}, \textit{Paediatric and Perinatal Epidemiology}, \textit{PLOS ONE}, \textit{Wisconsin Medical Journal}.} \\
    & \\
    & \textbf{Population Association of America} \\
    & Poster discussant, PAA Annual Meeting (2021) \\
    & \\
    & \textbf{Society for Pediatric and Perinatal Epidemiologic Research} \\
    & Program Planning Committee Member, SPER Annual Meeting (2023) \\
    & Abstract reviewer, SPER Annual Meeting (2020, 2021) \\
    & \\
    & \textbf{University of Wisconsin-Madison} \\
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Social Media Chair, Population Health Sciences Student Organization (2019-2020) \end{minipage} \\
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Abstract reviewer, Annual Student Poster Presentation Day, Department of Population Health\\ Sciences (March 2020) \end{minipage} \\	
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Panelist, Prospective Student Welcome Day Discussion Panel, Department of Population Health\\ Sciences (March 2020) \end{minipage} \\
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Organizer, Qualifying Exam Preparation Committee, Department of Population Health\\ Sciences (May 2020) \end{minipage} \\
    & \\
& \textbf{Wisconsin Medical Journal} \\
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Editorial Fellowship (2023-present) \end{minipage} \\
    & \begin{minipage}{6.15in}
	\everypar{\setlength\hangindent{1.5em}}Special issue advisory board member, ``Post-COVID 19: Lessons Learned From the Pandemic and Its Aftermath"
  (2023-present) \end{minipage} \\
    & \\
%%TRAINEESHIPS
\textsc{Traineeships} & Primary Care Research Fellowship, September 2022-Present \\
     & Department of Family Medicine \& Community Health \\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & \\
     & NICHD Predoctoral Training Program, September 2019-August 2021 \\
     & Center for Demography and Ecology \\
     & University of Wisconsin-Madison \\
     & \\
     & IRP Graduate Research Fellow, September 2018-August 2021 \\
     & Institute for Research on Poverty \\
     & University of Wisconsin-Madison \\
     & \\
%%RESEARCH EXPERIENCE
\textsc{Research} & Project Assistant to Professor Deborah Ehrenthal, 2016-2019 \\
\textsc{Positions} & Department of Obstetrics and Gynecology \\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & \\
& Research Assistant to Professor Elissa Ozanne, 2015-2016 \\
     & Dartmouth Institute for Health Policy and Clinical Practice \\
     & Dartmouth College Geisel School of Medicine \\
     & \\
%%TEACHING
\textsc{Teaching} & Teaching Assistant to Professor Marguerite Burns and Professor Rebecca Myerson, Spring 2021 \\
     & PHS 796: Introduction to Health Services Research \\
     & Department of Population Health Sciences \\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & \\
%%AWARDS
\textsc{Awards} 
     &\textbf{William E. Scheckler Award (2024)} \\
     & Deparment of Family Medicine \& Community Health \\
     & University of Wisconsin-Madison School of Meciein and Public Health \\
     & \textit{For an outstanding research publication as a postdoctoral trainee} \\
     & \\
     &\textbf{Finalist, Tyroler Prize Paper Award (2022)} \\
     & Society for Epidemiologic Research \\
     & \textit{For the best epidemiology paper submitted by a doctoral student} \\
     & \\
     &\textbf{IRP Graduate Research Fellow Conference Support (2019-2021)} \\
     & Institute for Research on Poverty \\
     & University of Wisconsin-Madison \\
     & \textit{Funding to present research at an academic conference} \\
     & \textit{(\$700 in 2019, \$200 in 2020, \$100 in 2021)} \\
     & \\
     &\textbf{Rankin/Skatrud Conference Award (2017)} \\
     & Department of Population Health Sciences \\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & \textit{\$1,000 fund to present research at an academic conference} \\
     & \\
     &\textbf{Outstanding New Student Award (2016)} \\
     & Department of Population Health Sciences \\
     & University of Wisconsin-Madison School of Medicine and Public Health \\
     & \textit{\$2,000 supplemental scholarship to support graduate studies} \\
     & \\
     &\textbf{James R. Turner Prize in Women's, Gender, and Sexuality Studies (2013)} \\
     & Department of Women's, Gender, and Sexuality Studies \\
     & College of Wooster \\
     & \textit{For the most distinguished senior thesis related to women's and gender studies across the College} \\
     & \\
     &\textbf{Anders Segerdahl Memorial Scholarship (2011-2013)} \\
     & Everett Smith Group, Ltd. \\
     & \textit{For exceptional collegiate academic performance} \\
     & \\
%%MEMBERSHIPS/AFFILIATIONS
\textsc{Memberships \&} & Population Association of America \\
\textsc{Affiliations} & Society for Epidemiologic Research \\
     & Society for Pediatric and Perinatal Epidemiologic Research \\
     & \\
%%TECH SKILLS
\textsc{Skills} & Statistical programming with Stata and SAS software. \LaTeX. Medicaid claims data management. \\
     & Lean Six Sigma Green Belt certification (2015).\\
\end{longtable}. 

\end{document}
